### 2022-12-15 definitions.tex
details

@@

@@

\begin{proposition}
There exist classes of WSTSs with strong upward compatibility for which there don't exist an algorithm computing an effective basis of $\uparrow post^*$.
\end{proposition}

\begin{proof}
Let us show that Reset VASS and LCS don't enjoy the property that $\uparrow post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow post^*$ for Reset VASS. Then, on ewould be able to decide whether $0$ is reachable in counter $i$ by examining if there is some vector $v$ in the basis such that $v(i)=0$. But reachability of $0$ in a counter $i$ is undecidable for Reset VASS. sont WSTS with strong compatibility. et l'accessibilité est undecidable.
$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\end{proof}

@@

\begin{theorem}(à prouver)
{\sc bounded resilience} is undecidable ??? for WSTS with upward compatibility and effective basis of $post^*$ ???
\end{theorem}

\begin{proof}
leur algorithme termine mais ne marche pas car l'intersection de post et J car ce n'est pas pertinent. et donc ???
\end{proof}

@@

\begin{proposition}(à prouver)
{\sc $k$-resilience}, hence {\sc bounded resilience}, is undecidable for effective WSTS with strong upward compatibility ????
\end{proposition}

\begin{proof}
pas de effective basis of $post^*$. leur algorithme n'est plus un algo. ex reset PN ?
\end{proof}

@@

\begin{proof} \alain{à relire/refaire}
Since reachability or liveness is undecidable for reset PN that are WSTS with strong monotony, from Proposition \ref{reductions}, we deduce that resilience is undecidable for WSTS with strong monotony.
\end{proof}

@@

\begin{corollary}
{\sc resilience} is decidable for context-free grammars.
\end{corollary}

Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} \alain{monotony ne semble pas strong...}avec $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) ???? resilience decidable.

>>>>

justification des definitions: si on enlève la condition  an upward-closed set $U$ (extended resilience $U$ qq) reachability reduces to resilience (avec $U=\{x\}$ donc indecidable pour les modèles à reachability indécidable.

et encore: renforcer sur l'hypothèses sur I, J tous les deux clos par le haut+bas.

@@

\begin{proof}
\textcolor{red}{à faire Mathieu}
\end{proof}

@@

\begin{proposition}
There exist classes of WSTSs with strong upward compatibility for which there don't exist an algorithm computing a basis of $\uparrow post^*$.
\end{proposition}

\begin{proof}
Let us show that Reset VASS and LCS don't enjoy the property that $\uparrow post^*$ is computable.
Suppose that one are able to compute a finite basis of $\uparrow post^*$ for Reset VASS. Then, on ewould be able to decide whether $0$ is reachable in counter $i$ by examining if there is some vector $v$ in the basis such that $v(i)=0$. But reachability of $0$ in a counter $i$ is undecidable for Reset VASS. sont WSTS with strong compatibility. et l'accessibilité est undecidable.
$\uparrow post^*$ n'est pas calculable pour les LCS non plus car $\uparrow post^*= \uparrow \downarrow post^*$ n'est pas calculable ???
\textcolor{red}{à relire par Mathieu}
\end{proof}

il existe des modèles où on peut calculer $\uparrow post^*$: inserted channel systems: on sait calculer $post^*$ qui est rationnel donc on sait calculer $\uparrow post^*$.

@@

\begin{proposition}(à prouver)
 leur algorithme for {\sc bounded resilience} termine mais pas correct for WSTS with upward compatibility, not necessarly strong, and an effective basis of $post^*$ ?
\end{proposition}

\begin{proof}
leur algorithme termine mais pas correct car l'intersection de post et J car alors le lemmme xxxx est faux (contre-exemple)
 \textcolor{red}{à faire Mathieu}
\end{proof}

\begin{theorem}(à prouver)
{\sc bounded resilience} is undecidable ??? for WSTS with upward compatibility, not necessarly strong, and an effective basis of $post^*$ ???
\end{theorem}

\begin{proof}
 \textcolor{red}{à faire Mathieu}
\end{proof}

@@

\begin{proposition}(à prouver)
{\sc $k$-resilience}, hence {\sc bounded resilience}, is undecidable for effective WSTS with strong upward compatibility but without basis of post* ????
\end{proposition}

\begin{proof}
pas de effective basis of $post^*$. leur algorithme n'est plus un algo. ex reset PN ?  \textcolor{red}{à faire Mathieu}
\end{proof}

@@

\begin{proof} \alain{à relire/refaire}
Since liveness is undecidable for reset PN that are WSTS with strong monotony, from Proposition \ref{reductions}, we deduce that resilience is undecidable for WSTS with strong monotony.
  \textcolor{red}{à faire Mathieu}
\end{proof}

Let us deduce that effective basis of $post^*$ ex reset PN ?

@@

\begin{corollary}
{\sc resilience} is decidable for finite automata and context-free grammars (seen as transition systems)
\end{corollary}

  \textcolor{red}{à faire Mathieu}
Context-free grammars are WSTS \cite{DBLP:journals/tcs/FinkelS01} \alain{monotony ne semble pas strong...}avec $\uparrow post^*$ calculable (because the reachability set of a pushdown machine is an effectively computable regular language) ???? resilience decidable.
\end{proof}
